The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-11-28 Paper.Rmd
responses on the Data section, Shya please look at one comment in particular

@@

<!--***DAN: Shya, make this an autolink to the number of data points - 5930, but should be an autolink, so if the number changes it updates
***Shya: Done.-->

@@

@@

<!--***DAN: Shya to add a figure shwoing the locations on a map of the UK and cite it here with an automatic citation
***Shya: It is already in suppmat figure S1.-->

@@

<!--***DAN: Shya, let's discuss please - if we say this we have to be sure we did *exactly* the same pre-processing as Lawrence, whereas I seem to remember we did something slightly different-->

>>>>

<!--***DAN: Can you check this please? I do not think it can be right. The values on Fig. 3a range from close to 0 to over 3000. 3000 would be 3000 Mg C. I do not think a cubic meter of soil even weighs that much, including all the carbon and non-carbon components.-->

@@

@@

<!--***DAN: Yes, that makes sense, but please go back to the data as published, which should be a supporting appendix to the original publications, and make sure I have not given you erroneous data-->

@@

@@
